---
title: "`r params$curr_pd` `r params$cntry` COP Priorities Supporting Visualizations"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
format: pptx
execute:
  echo: FALSE
params: 
  curr_pd: "FY22Q4"
  cntry: "Malawi"
  agency: "USAID"
editor: 
  markdown: 
    wrap: 72
---

```{r}
# | label: setup
# | include: FALSE
# | cache: TRUE

# DEPENDENCIES ------------------------------------------------------------
  
  library(tidyverse)
  library(gagglr)
  library(glue)
  library(scales)
  library(extrafont)
  library(tidytext)
  library(patchwork)
  library(ggtext)
  library(googlesheets4)
  library(mindthegap)
  library(ggrepel)
  library(janitor)
  library(sf)
  library(selfdestructin5)
  library(gt)
  library(cascade) # Use dev version
  library(ggpattern)
  library(rcartocolor)
  library(here)
  library(assertr)

# SOURCE LOCAL FUNCTIONS --------------------------------------------------

  source(here("Scripts/01_achievement_indicator-psnu.R"))
  source(here("Scripts/02_95s_epi.R"))
  source(here("Scripts/03_prevalence-gaps_gp-psnu-sex.R"))
  source(here("Scripts/04_populationpyramid.R"))
  source(here("Scripts/05_testing.R"))
  source(here("Scripts/06_linkage_psnu.R"))
  source(here("Scripts/07_txcoverage_age_sex.R"))
  source(here("Scripts/08_vl-coverage-and-suppression_gp-age.R"))
  source(here("Scripts/09_vl-coverage-and-suppression_gp-psnu.R"))
  source(here("Scripts/10_prep-trends_age-sex-kp.R"))
  source(here("Scripts/11_sid_comp.R"))
  source(here("Scripts/12_budget-trends_agency.R"))
  source(here("Scripts/13_funding-distro_funding-flavors.R"))
  source(here("Scripts/14_hrh-footprint-various.R"))
  source(here("Scripts/15_10s_barriers.R"))
  source(here("Scripts/16_hrh-titles.R"))
  source(here("Scripts/17_vl-coverage-and-suppression_kp-psnu.R"))
  source(here("Scripts/18_ovc-coverage_psnu.R"))
  source(here("Scripts/19_ovc-budget_agency.R"))
  source(here("Scripts/20_DREAMS_prev-gaps_psnu.R"))
  source(here("Scripts/20_tbstat_coverage.R"))
  source(here("Scripts/99_utilities.R"))
```

```{r}
# | label: load_data
# | include: FALSE
# | cache: TRUE

  source(here("Scripts/91_setup.R"))

```

### Purpose

In advance of the PLLs and COP meetings starting the week of February 13, the OHA/SIEI division wanted to provide some useful data points that may help as a launching point to these discussions and help hasten further exploration. The visuals provided here aim to provide a first step in identifying gaps and a baseline as they relate to COP priorities informed by Ambassador Nkengasong's [PEPFAR Strategy (5x3 pillars)](https://www.state.gov/reimagining-pepfar-at-20-to-end-the-hiv-aids-pandemic-by-2030/).

These supporting visuals are intended to help create and inform initial discussion and prompt further data exploration. We have provided notes, data sources, and calculations for anything included here to make this a jumping off point to delve into any software and explore further. If you have questions, please contact your SIEI backstop for assistance. Underlying R code can be found on [GitHub](https://github.com/USAID-OHA-SI/hardapoart)

```{r}
# | label: supplemental_text

sup_text <- glue("Note that the visuals below largely reflect the {params$cntry} as a whole or all PEPFAR agencies unless otherwise noted in the visual itself.")
  
```

`r if(params$agency == "PEPFAR"){sup_text}`

```{r}
# | label: achievement
# | include: FALSE 
  
  df_msd %>%
    prep_achv_psnu(params$cntry,params$agency) %>%
    viz_achv_psnu()
```

```{r}
# | label: epi_95s

  viz_unaids_all(params$cntry)

```

```{r}
#| label: prevalence

df_natsubnat %>% 
  prep_hiv_prevalence(params$cntry, "POP") %>% 
  viz_hiv_prevalence()

  
```

```{r}
#| label: prevalence_dreams

df_natsubnat %>% 
  prep_hiv_prev_DREAMS(params$cntry) %>% 
  viz_hiv_prevalence()

```

```{r}
# | label: youth_bulge

df_natsubnat %>% 
  prep_pop_pyramid(params$cntry, "country") %>% 
  viz_pop_pyramid()

```

```{r}
# | label: youth_bulge_dreams

df_natsubnat %>% 
  prep_pop_pyramid(params$cntry, "psnu") %>% 
  prep_pop_pyramid_dreams(df_msd) %>% 
  viz_pop_pyramid(type = "DREAMS")

```

```{r}
# | label: testing

 prep_modality_age(df_msd, params$cntry, "PEPFAR", trendscoarse) %>% 
   viz_modality_age()

```


```{r}
# | label: ovc_tx

prep_ovc_coverage(df_msd, df_subnat, params$cntry, "PEPFAR") %>% 
  viz_ovc_coverage()

```


```{r}
# | label: linkage

df_msd %>% 
  prep_linkage_psnu(params$cntry, params$agency) %>% 
  viz_linkage_psnu()

```


```{r}
# | label: tx_gap
# | execute: warning: FALSE

viz_tx_all(params$cntry, params$agency) 


```

```{r}
# | label: vlsc_pop

df_msd %>%
  prep_viral_load(params$cntry, params$agency) %>%
  viz_viral_load()

```

```{r }
# | label: vlsc_kp

df_msd %>% 
  prep_viral_load_kp_agyw(params$cntry, params$agency) %>% 
  viz_viral_load_kp_agyw()

```


```{r}
# | label: vlsc_geo

df_msd %>%
  prep_viral_load_psnu(params$cntry, params$agency) %>%
  viz_viral_load_psnu()

```

```{r}
# | label: prep

suppressMessages(
  df_msd %>%
    prep_prep_disagg(params$cntry, params$agency) %>%
    viz_prep_disagg() %>% 
    print()
)
```


```{r}
# | label: sid

df_sid %>%
  prep_sid(params$cntry) %>%
  viz_sid()
```


```{r}
# | label: budget_share

df_fsd %>%
  prep_budget_trends(params$cntry) %>%
  viz_budget_trends()

```


```{r}
# | label: ovc_budget

df_msd %>% 
  prep_ovc_budget(df_fsd, params$cntry) %>% 
  viz_ovc_budget()

```


```{r}
#| label: funding_distro

df_fsd %>%
  prep_funding_distro(params$cntry, "USAID") %>%
  viz_funding_distro()

```


```{r}
#| label: staffing_footprint

df_hrh %>%
  prep_hrh_footprint(params$cntry, params$agency) %>%
  viz_hrh_footprint()
```


```{r}
#| label: staffing_titles

df_hrh %>%
  prep_hrh_titles(params$cntry, params$agency) %>%
  viz_hrh_titles()
```

```{r}
#| label: 10-10-10 barriers

df_tens %>%
  prep_10s_barriers(params$cntry) %>%
  viz_10s_barriers()
```

### Calculations Used

*Calculations*

**HIV Prevalence** 
  - Data Source: MSD 
  - PLHIV / Population

**OVC Budget**
  - Data Source: FSD
  - Total COP Allocation for OVC beneficiaries
  
**OVC Coverage of CLHIV**
  - Data Sources: MSD + NAT_SUBNAT MSD
  - OVC_HIVSTAT_POS (Receiving ART, <15) / PLHIV (<15)
    - Only in OVC Programed PSNUs 
    
**OVC Coverage of Children on Treatment**
  - Data Sources: MSD
  - OVC_HIVSTAT_POS (Receiving ART, <15) / TX_CURR (Age/Sex/HIVStatus, <15)
    - Only in OVC Programed PSNUs 
    
**OVC Programmed PSNU**
  - Data Source: MSD
  - PSNUs where there is a OVC programming - OVC_HIVSTAT Total Numerator > 0

**Proxy Linkage**
  - Data Source: MSD
  - TX_NEW / HTS_TST_POS
  
**Undiagnosed** 
  - Data Source: UNAIDS 
  - PLHIV - PLHIV with Known Status

**Target Achievement** 
  - Data Source: MSD 
  - FY Cumulative Results / FY Targets

**Treatment Coverage Status** 
  - Data Source: NAT_SUBNAT MSD 
  - Diagnosed / PLHIV

**Treatment Gap** 
  - Data Source: NAT_SUBNAT MSD 
  - TX_CURR_SUBNAT / PLHIV

**Viral Load Coverage** 
  - Data Source: MSD 
  - TX_PVLS_D / TX_CURR (2 periods prior)

**Viral Load Suppression** 
  - Data Source: MSD 
  - TX_PVLS / TX_PVLS_D

*Adjustments*

**AGYW Grouping**
  - Data Source: MSD
  - 10-24 Females 
  
**GenPop Grouping**
  - Data Source: MSD
  - Total Numerator - KeyPoP (min = 0)
  
**Modality Groupings** 
  - Data Source: MSD 
  - Prevention = PMTCT ANC, Post ANC1, VMMC 
  - Case Finding = All other modalities

**OVC_SERV Target Adjustment**
  - Data Source: MSD
  - OVC_SERV disaggs excluding Age/Sex/DREAMS
  
**Remove Known Issues** 
  - Data Sources: MSD and FSD 
  - Removes all flagged known issues flagged by SI and ER country backstops 
  - Source doc: https://docs.google.com/spreadsheets/d/1CMPY-GCWP3NSNWvLGLwMwBaPZsobgvjtobhjkZkDfow/edit#gid=1630220016 
  - Source owners: OHA/SIEI/SI

**Remove M&O** 
  - Data Source: FSD 
  - Keep only where record_type == "Implementing Mechanism"

**Remove SCH** 
  - Data Source: FSD 
  - Remove all SCH and SGAC flagged supply chain mechanisms 
  - Source doc: https://docs.google.com/spreadsheets/d/1mCJWDo4FPW2cQ6LpbsSjtnRjT7sUpPEOqxfT2zQNo64/edit#gid=1369222419 
  -Source owners: OHA/SIEI/ER

**Funding Type Groupings** 
  - Data Sources: FSD and HRH SD 
  - Site Level Non-SD = interaction_type either Non Service Delivery or Non-Service Delivery 
  - Service Delivery = interaction_type == Direct Service Delivery 
  - All others are their program type -

### Data Sources

**Financial_Structured_Datasets_COP17-22_20221216**
  - Date accessed: 2023-02-23
  - Date on data source: 2023-02-10
  - Original Location: PEPFAR Panorama - https://pepfar-panorama.org/forms/downloads/
  - Google Drive ID: NA
  
**HIV Policy Lab - Policy Data**
  - Date accessed: 2021-11-09
  - Date on data source: 2021-09-17
  - Original Location: HIV Policy Lab - https://www.hivpolicylab.org/data
  - Google Drive ID: 1LadXX9g9D6MCp6M3WD27Js85YE8MHrf_ulJQmRVduCU
  
**HRH_Structured_Datasets_Site_IM_FY21-22_not_redacted_20230118_PostClean_Adjusted (1)**
  - Date accessed: 2023-02-06
  - Date on data source: 2023-01-31
  - Original Location: contact J.Roffenbender & sign terms of use
  - Google Drive ID: 1IhiXVtH0DUofXOXF0KL0ikzfdT0ROmBq
  
**MER_Structured_Datasets_PSNU_IM_FY21-23_20230210_v1_1**
  - Date accessed: 2023-02-23
  - Date on data source: 2023-02-10
  - Original Location: PEPFAR Panorama - https://pepfar-panorama.org/forms/downloads/
  - Google Drive ID: NA
  
**MER_Structured_Datasets_NAT_SUBNAT_FY15-22_20221216_v2_1**
  - Date accessed: 2023-01-17
  - Date on data source: 2023-02-10
  - Original Location: PEPFAR Panorama - https://pepfar-panorama.org/forms/downloads/
  - Google Drive ID: NA
  
**SID_Global_Dataset Final 2.0**
  - Date accessed: 2023-02-02
  - Date on data source: 2022-06-08
  - Original Location: PEPFAR Sharepoint - https://pepfar.sharepoint.com/sites/SustainabilityAnalysisCOP22/Shared%20Documents/Global%20Dataset/SID_Global_Dataset%20Final%202.0.xlsx
  - Google Drive ID: 1nn4c9NBsYchD6xUjimbWBB-4tHvrc4-AnWntGOk0XLc
  
**UNAIDS - AIDSinfo Global data on HIV epidemiology and response**
  - Date accessed: 2023-02-09
  - Date on data source: 2022-08-10
  - Original Location: AIDSInfo
  - Google Drive ID: 1k5j169a_MtecrMdsu_n870Y0Y8tezLPopULn7AP3lQQ