---
title: "country report"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
format: pptx
execute:
  echo: FALSE
params: 
  curr_pd: "FY22Q4"
  cntry: "Malawi"
  agency: "USAID"

---

```{r}
# | label: setup
# | include: FALSE

glue("{params$cntry}")
```

## Purpose

TODO - fill with: - purpose statement/intent - what this is/isn't - contact info

## 1. Are there any major gaps in achievement as of `params$curr_pd`?

## 2. Is progress being made in reaching epidemic control? Are there gaps in the 95s that can be targeted?

## 3. What does HIV prevalence look like across sex / SNUs? by age/sex bands?

## 11. Are there key gaps identified by the SID for the country to prioritize?

```{r}
# | label: sid

df_sid %>% 
  prep_sid(params$cntry) %>% 
  viz_sid()
```
## 12. Have COP budgets been flatlining or changing in a similar manner across agencies?

```{r}
# | label: budget_share

df_fsd %>% 
  prep_budget_trends(params$cntry) %>% 
  viz_budget_trends()

```

## 13. Does the country have the optimal mix of PEPFAR spending when thinking about sustainability?

```{r}
#| label: funding_distro

df_fsd %>% 
  prep_funding_distro(params$cntry, param$agency) %>% 
  viz_funding_distro()

```

## 14. What does the current staffing footprint look like in country? How do they align with sustainability and leveraging our assets?

```{r}
#| label: staffing_footprint

df_hrh %>% 
  prep_hrh_footprint(params$cntry, param$agency) %>% 
  viz_hrh_footprint()
```

## 15

## 16. What are the large staffing categories? How do they align with sustainability and leveraging our assets?

```{r}
#| label: staffing_titles

df_hrh %>% 
  prep_hrh_titles(params$cntry, param$agency) %>% 
  viz_hrh_titles()
```

## Calculations Used

TODO

## Data Sources

TODO
