---
title: "country report"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
format: pptx
execute:
  echo: FALSE
params: 
  curr_pd: "FY22Q4"
  cntry: "Malawi"

---

```{r}
# | label: setup
# | include: FALSE

glue("{params$cntry}")
```

## Purpose

TODO - fill with: - purpose statement/intent - what this is/isn't - contact info

## 1. Are there any major gaps in achievement as of `params$curr_pd`?

```{r}
# | label: achievement
  df_msd %>%
        prep_achv_psnu(params$cntry,params$agency) %>%
        viz_achv_psnu(params$cntry,params$agency)
```  
  

## 2. Is progress being made in reaching epidemic control? Are there gaps in the 95s that can be targeted?

## 3. What does HIV prevalence look like across sex / SNUs? by age/sex bands?

## 10. Is PrEP uptake relatvely constant across demographics? 

```{r}
# | label: prep
df_msd %>%
    prep_prep_disagg(params$cntry,params$agency) %>%
    viz_prep_disagg(params$cntry,params$agency)
```


## 11. Are there key gaps identified by the SID for the country to prioritize?

```{r}
# | label: sid

df_sid %>% 
  prep_sid(params$cntry) %>% 
  viz_sid()
```
## 12. Have COP budgets been flatlining or changing in a similar manner across agencies?

```{r}
# | label: budget_share

df_fsd %>% 
  prep_budget_trends(params$cntry) %>% 
  viz_budget_trends()

```

## 13. Does the country have the optimal mix of PEPFAR spending when thinking about sustainability?

```{r}
#| label: funding_distro

df_fsd %>% 
  prep_funding_distro(params$cntry, "USAID") %>% 
  viz_funding_distro()

```

## 14. What does the PEPFAR funding staffing footprint look like?
```{r}
#| label: staffing_footprint

df_hrh %>% 
  prep_hrh_footprint(params$cntry) %>% 
  viz_hrh_footprint()
```


## Calculations Used

TODO

## Data Sources

TODO
