---
title: "`r params$curr_pd` `r params$cntry` COP Priorities Supporting Visualizations"
date: "Generated: `r format(Sys.time(), '%Y-%m-%d')`"
output: 
  html_document:
    fig_width: 10
    fig_height: 5.625
    dpi: 330
params: 
  curr_pd: "FY23Q1"
  cntry: "Malawi"
  agency: "USAID"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r functions, include=FALSE}

# SOURCE LOCAL FUNCTIONS --------------------------------------------------

  source(here("Scripts/01_achievement_indicator-psnu.R"))
  source(here("Scripts/02_95s_epi.R"))
  source(here("Scripts/03_prevalence-gaps_gp-psnu-sex.R"))
  source(here("Scripts/04_populationpyramid.R"))
  source(here("Scripts/05_testing.R"))
  source(here("Scripts/06_linkage_psnu.R"))
  source(here("Scripts/07_txcoverage_age_sex.R"))
  source(here("Scripts/08_vl-coverage-and-suppression_gp-age.R"))
  source(here("Scripts/09_vl-coverage-and-suppression_gp-psnu.R"))
  source(here("Scripts/10_prep-trends_age-sex-kp.R"))
  source(here("Scripts/11_sid_comp.R"))
  source(here("Scripts/12_budget-trends_agency.R"))
  source(here("Scripts/13_funding-distro_funding-flavors.R"))
  source(here("Scripts/14_hrh-footprint-various.R"))
  source(here("Scripts/15_hrh-titles.R"))
  source(here("Scripts/16_10s_barriers.R"))
  source(here("Scripts/17_vl-coverage-and-suppression_kp-psnu.R"))
  source(here("Scripts/18_ovc-coverage_psnu.R"))
  source(here("Scripts/19_ovc-budget_agency.R"))

# Helper function for assertr::verify() to show more descriptive error messages
  err_text <- function(msg) stop(msg, call = FALSE)

```

### Purpose

In advance of the PLLs and COP meetings starting the week of February
13, the OHA/SIEI division wanted to provide some useful data points that
may help as a launching point to these discussions and help hasten
further exploration. The visuals provided here aim to provide a first
step in identifying gaps and a baseline as they relate to COP priorities
informed by Ambassador Nkengasong's [PEPFAR Strategy (5x3 pillars)](https://www.state.gov/reimagining-pepfar-at-20-to-end-the-hiv-aids-pandemic-by-2030/).

These supporting visuals are intended to help create and inform initial
discussion and prompt further data exploration. We have provided notes,
data sources, and calculations for anything included here to make this a
jumping off point to delve into any software and explore further. If you
have questions, please contact your SIEI backstop for assistance. Underlying R code can be found on [GitHub](https://github.com/USAID-OHA-SI/hardapoart)

```{r sup_text, include=FALSE}
sup_text <- glue("Note that the visuals below largely reflect {params$cntry} as a whole or all PEPFAR agencies unless otherwise noted in the visual itself.")
  
```

`r if(params$agency == "PEPFAR"){sup_text}`

### 1. Are there any major gaps in achievement as of `r params$curr_pd`?

```{r achievement}

df_msd %>%
  prep_achv_psnu(params$cntry,params$agency) %>%
  viz_achv_psnu()

```

### 2. Is progress being made in reaching epidemic control? Are there gaps in the 95s that can be targeted?

```{r epi_95s}

viz_unaids_all(params$cntry)

```

### 3. What does HIV prevalence look like across sex / SNUs?

```{r prevalence}

df_natsubnat %>% 
  prep_hiv_prevalence(params$cntry) %>% 
  viz_hiv_prevalence()
  
```

### 4. Is there a youth bulge of PLHIV we need to plan for?

```{r youth_bulge}

df_natsubnat %>% 
  prep_pop_pyramid(params$cntry) %>% 
  viz_pop_pyramid()

```

### What proportion of C/ALHIV is the OVC Comprehensive program reaching?

```{r ovc_tx}

prep_ovc_coverage(df_msd, df_subnat, params$cntry, "PEPFAR") %>% 
  viz_ovc_coverage()

```


### 5. Does testing favor prevention or case finding and does this fit with where `r params$cntry` is in the epidemic?

```{r testing}

 prep_modality_age(df_msd, params$cntry, "PEPFAR", trendscoarse) %>% 
   viz_modality_age()

```

### 6. Are there any major issues with proxy linkage by geography/population that can be targeted?

```{r linkage}

df_msd %>% 
  prep_linkage_psnu(params$cntry, params$agency) %>% 
  viz_linkage_psnu()

```

### 7. Are new patients being added to the areas with the largest gaps in treatment coverage?

```{r tx_gap, warning=FALSE}

viz_tx_all(params$cntry, params$agency) 

```

### 8. Are certain populations by age or sex being missed when trying to reach the 3rd 95?

```{r vlsc_pop}

df_msd %>% 
  prep_viral_load(params$cntry, params$agency) %>% 
  viz_viral_load()

```

### 9. Are certain populations groups being missed when trying to reach the 3rd 95?

```{r vlsc_kp}

df_msd %>% 
  prep_viral_load_kp_agyw(params$cntry, params$agency) %>% 
  viz_viral_load_kp_agyw()

```

### 10. Are certain regions by age or sex being missed when trying to reach the 3rd 95?

```{r vlsc_geo}

df_msd %>% 
  prep_viral_load_psnu(params$cntry, params$agency) %>% 
  viz_viral_load_psnu()

```


### 11. Is PrEP uptake relatively consistent across demographics?

```{r prep}

df_msd %>%
    prep_prep_disagg(params$cntry, params$agency) %>%
    viz_prep_disagg()
```

### 12. Are there key gaps identified by the SID for `r params$cntry` to prioritize?

```{r sid}

df_sid %>% 
  prep_sid(params$cntry) %>% 
  viz_sid()

```

### 13. Have COP budgets been flatlining or changing in a similar manner across agencies?

```{r budget_share}

df_fsd %>% 
  prep_budget_trends(params$cntry) %>% 
  viz_budget_trends()

```

### Are OVC target increases proportional to changes in the OVC budget?

```{r ovc_budget}

df_msd %>% 
  prep_ovc_budget(df_fsd, params$cntry) %>% 
  viz_ovc_budget()

```


### 14. Does `r params$cntry` have the optimal mix of PEPFAR spending when thinking about sustainability?

```{r funding_distro}

df_fsd %>% 
  prep_funding_distro(params$cntry, "USAID") %>% 
  viz_funding_distro()

```

### 15. What does the current staffing footprint look like in `r params$cntry`? How do they align with sustainability and leveraging our assets?

```{r staffing_footprint}

df_hrh %>% 
  prep_hrh_footprint(params$cntry, "USAID") %>% 
  viz_hrh_footprint()

```

### 16. What are the large staffing categories? How do they align with sustainability and leveraging our assets?

```{r staffing_titles}

df_hrh %>% 
  prep_hrh_titles(params$cntry, "USAID") %>% 
  viz_hrh_titles()

```

### 17. What are the gaps in adopting structural laws and policies towards the UNAIDS 10-10-10 goals?

```{r 10s_barriers}

df_tens %>% 
  prep_10s_barriers(params$cntry) %>% 
  viz_10s_barriers()

```

### Calculations Used

*Calculations*

**HIV Prevalence** 
  - Data Source: MSD 
  - PLHIV / Population

**OVC Budget**
  - Data Source: FSD
  - Total COP Allocation for OVC beneficiaries
  
**OVC Coverage of CLHIV**
  - Data Sources: MSD + NAT_SUBNAT MSD
  - OVC_HIVSTAT_POS (Receiving ART, <15) / PLHIV (<15)
    - Only in OVC Programed PSNUs 
    
**OVC Coverage of Children on Treatment**
  - Data Sources: MSD
  - OVC_HIVSTAT_POS (Receiving ART, <15) / TX_CURR (Age/Sex/HIVStatus, <15)
    - Only in OVC Programed PSNUs 
    
**OVC Programmed PSNU**
  - Data Source: MSD
  - PSNUs where there is a OVC programming - OVC_HIVSTAT Total Numerator > 0
  
**Proxy Linkage**
  - Data Source: MSD
  - TX_NEW / HTS_TST_POS
  
**Undiagnosed** 
  - Data Source: UNAIDS 
  - PLHIV - PLHIV with Known Status

**Target Achievement** 
  - Data Source: MSD 
  - FY Cumulative Results / FY Targets

**Treatment Coverage Status** 
  - Data Source: NAT_SUBNAT MSD 
  - Diagnosed / PLHIV

**Treatment Gap** 
  - Data Source: NAT_SUBNAT MSD 
  - TX_CURR_SUBNAT / PLHIV

**Viral Load Coverage** 
  - Data Source: MSD 
  - TX_PVLS_D / TX_CURR (2 periods prior)

**Viral Load Suppression** 
  - Data Source: MSD 
  - TX_PVLS / TX_PVLS_D

*Adjustments*

**AGYW Grouping**
  - Data Source: MSD
  - 10-24 Females 
  
**GenPop Grouping**
  - Data Source: MSD
  - Total Numerator - KeyPoP (min = 0)
  
**Modality Groupings** 
  - Data Source: MSD 
  - Prevention = PMTCT ANC, Post ANC1, VMMC 
  - Case Finding = All other modalities

**OVC_SERV Target Adjustment**
  - Data Source: MSD
  - OVC_SERV disaggs excluding Age/Sex/DREAMS
  
**Remove Known Issues** 
  - Data Sources: MSD and FSD 
  - Removes all flagged known issues flagged by SI and ER country backstops 
  - Source doc: https://docs.google.com/spreadsheets/d/1CMPY-GCWP3NSNWvLGLwMwBaPZsobgvjtobhjkZkDfow/edit#gid=1630220016 
  - Source owners: OHA/SIEI/SI

**Remove M&O** 
  - Data Source: FSD 
  - Keep only where record_type == "Implementing Mechanism"

**Remove SCH** 
  - Data Source: FSD 
  - Remove all SCH and SGAC flagged supply chain mechanisms 
  - Source doc: https://docs.google.com/spreadsheets/d/1mCJWDo4FPW2cQ6LpbsSjtnRjT7sUpPEOqxfT2zQNo64/edit#gid=1369222419 
  -Source owners: OHA/SIEI/ER

**Funding Type Groupings** 
  - Data Sources: FSD and HRH SD 
  - Site Level Non-SD = interaction_type either Non Service Delivery or Non-Service Delivery 
  - Service Delivery = interaction_type == Direct Service Delivery 
  - All others are their program type -

### Data Sources

**DATIM GENIE MER PSNU By IM** 
  - Date accessed: 2023-02-16 
  - Date on data source: 2023-02-10 
  - Original Location: DATIM GENIE - https://www.datim.org/api/apps/Genie/ 
  - Google Drive ID: 1JMsTOxt-LUm61newJbMDsFrh-DNAfG72

**Financial_Structured_Datasets_COP17-22_20221216** 
  - Date accessed: 2023-01-17 - Date on data source: 2022-12-16 
  - Original Location: PEPFAR Panorama 
  - https://pepfar-panorama.org/forms/downloads/ 
  - Google Drive ID: NA

**HIV Policy Lab - Policy Data** 
  - Date accessed: 2021-11-09 
  - Date on data source: 2021-09-17 
  - Original Location: HIV Policy Lab - https://www.hivpolicylab.org/data 
  - Google Drive ID: 1LadXX9g9D6MCp6M3WD27Js85YE8MHrf_ulJQmRVduCU

**HRH_Structured_Datasets_Site_IM_FY21-22_not_redacted_20230118_PostClean_Adjusted (1)** 
- Date accessed: 2023-02-06 
- Date on data source: 2023-01-31 
- Original Location: contact J.Roffenbender & sign terms of use
- Google Drive ID: 1IhiXVtH0DUofXOXF0KL0ikzfdT0ROmBq

**MER_Structured_Datasets_NAT_SUBNAT_FY15-22_20221216_v2_1** 
  - Date accessed: 2023-01-17 
  - Date on data source: 2022-12-16 
  - Original Location: PEPFAR Panorama - https://pepfar-panorama.org/forms/downloads/ 
  - Google Drive ID: NA

**SID_Global_Dataset Final 2.0** 
  - Date accessed: 2023-02-02 
  - Date on data source: 2022-06-08 
  - Original Location: PEPFAR Sharepoint - https://pepfar.sharepoint.com/sites/SustainabilityAnalysisCOP22/Shared%20Documents/Global%20Dataset/SID_Global_Dataset%20Final%202.0.xlsx 
  - Google Drive ID: 1nn4c9NBsYchD6xUjimbWBB-4tHvrc4-AnWntGOk0XLc

**UNAIDS - AIDSinfo Global data on HIV epidemiology and response** 
  - Date accessed: 2023-02-09 
  - Date on data source: 2022-08-10 
  - Original Location: AIDSInfo
  - Google Drive ID: 1k5j169a_MtecrMdsu_n870Y0Y8tezLPopULn7AP3lQQ
